Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2017-12-29 survey/survey.tex
Data II continuance

@@

Of course, one does not get a programming language with just (typed)
constants!

>>>>

Of course, one does not get a programming language with just typed
constants! There is a need to perform multiple equivalences. There are
in fact three ways to do this: sequential composition $\odot$, 
choice composition $\oplus$ (sometimes called juxtaposition) and parallel
composition $otimes$. See Figure~\ref{pi-combinators} for the signatures.

$c_1 \odot c_2$ corresponds to performing $c_1$ first, then $c_2$, and
is the usual notion of composition -- and corresponds to $\fatsemi$ of
the language of the previous section. $c_1 \oplus c\_2$ chooses to
perform $c_1$ or $c_2$ depending on whether the input is labelled
$\textsf{inl}$ or $\textsf{inr}$ respectively. $c_1 \otimes c_2$
operates on a product structure, and applies $c_1$ to the first component
and $c_2$ to the second.

@@
